\documentclass[../paper.tex]{subfiles}

\begin{document}

For small and medium businesses, probably the most important aspect when
choosing a data warehouse system is cost, both for the initial development and
for the ongoing maintenance of such a system.

Nowadays, software as a service (SaaS) can provide many advantages over
traditional services. The pay-as-you-go model is very friendly towards small
businesses which could not otherwise easily justify the upfront cost for
servers and related costs for hosting a data warehouse.

This means that, in many cases, SaaS is the most cost-effective and also the
simplest solution for small businesses to opt for. When comparing them to
traditional services, SaaS products virtually don't need any setup time and
can be deployed instantly.

In the case of data warehouse systems, SaaS is also commonly referred to as
data warehouse as a service (DWaaS).

Given the advantages above, we focus in this section on some concrete DWaaS
products and review what they have in common, how they differ and whether they
are in fact suitable for small businesses.

\subsection{Segment (by Twilio)}

Segment is a customer data platform for collecting, cleaning and controlling
data across multiple services in one central location. It offers a
\textit{Free} plan which supports two data sources, 1,000 API calls and more
than 300 integrations, a \textit{Team} plan starting at \$120/month for 10
users with unlimited data sources and 10,000 API calls up to \$1,125/month for
100,000 API calls, and a \textit{Business} plan for custom usage requirements.
The scalable \textit{Team} plan should be sufficient for most SMEs.

After first logging into Segment, the user can choose the team they are working
on (Engineering, Marketing, Founder/Executive, Product, Analytics) and select
the first data source, e.g. a website, programming language or HTTP API. Next,
data destinations have to be selected, e.g. Google Analytics, Intercom, etc.
Finally, the user gets to the dashboard, which provides an overview of all data
sources and destinations and a way to add new ones.

In total, Segment supports 98 different data sources and 650 data destinations
at the time of writing. Additionally, creating custom data sources and
destinations by building JavaScript function that access the corresponding API.
Also, by supporting programming languages as data source and webhooks as data
destinations, virtually any software can be integrated.

Segment does not offer any analytics capability on its own but is meant to
simplify data collection and distribution by managing all data sources and
destinations in a single place, therefore reducing complexity and increasing
flexibility. For example, website analytics can be switched from
Google~Analytics~\cite{google_analytics} to GoSquared~\cite{gosquared} without
changing the website itself.

\subsection{Panoply}

Panoply is a data warehouse solution built on AWS Redshift and offers four
plans: \textit{LITE}, \textit{STARTER}, \textit{PRO} and \textit{BUSINESS}. The
last of them is specifically aimed at SMBs, according to their own website.
There is a free version available for testing which has the functionality of
the \textit{LITE} plan for a period of 14 days. After logging in for the first
time, the website prompts the user to create a data warehouse with a unique
name. Next, the user is prompted with the possibility of adding a data source,
which can also be skipped. Afterwards, the user has full access to the
instance.

Panoply offers 122 data sources that have been integrated by the Panoply team.
Additionally, there are 131 data sources which are developed by partners that
can be added. In total, 253 different data sources are supported. To analyse
the collected data, Panoply offers the integration of 43 visualisation tools,
of which 42 are BI tools.

Panoply is a full solution to synchronise, store and access a company’s data
while also providing analytical features. In addition to the supported
visualisation tools, data can be structured and viewed in a traditional tabular
form.

The different pricing tiers are differentiated by three main parts: amount of
data sources, storage space and support. The suggested SMB solution, called the
\textit{BUSINESS} plan, includes 10 distinct data sources, 100 GB of storage
and support with a reaction time of less than an hour. It also includes data
governance features, yet the storage itself is based in the USA, without any
other option. All plans offer an unlimited amount of users. More storage and
data sources is possible for the \textit{Enterprise} plan, which is adaptive to
a company’s needs. This adds the possibility of storing the data in one of 19
different countries.

\subsection{Tableau}

Tableau is a visualisation software which mainly focuses on data visualisation
and data reporting. This tool is founded by Tableau Software and is now owned
by the cloud computing solutions company Salesforce.com. Tableau uses a
machine-learning based analysis engine which helps model automated structured
data tables and displays statistical findings.

Analytics or Business Intelligence is a cycle with different steps:
Transactions need to be stored securely before data analysts periodically
analyse the data. Afterwards, these insights are shared across the company
where then senior colleagues make decisions before the outcomes get monitored
from managers who change product offers. Tableau has six key products which
aim at improving the workflow for every of the six previously mentioned steps
by offering a simple to use, connected platform.

For storing data, Tableau does not use a dedicated database but a special file
type called \texttt{.tde} or more recent \texttt{.hyper}. Since data is not
stored correctly all time due to a missing category or a wrong scanned item,
these mistakes need to be fixed manually every time or in bulk periodically.
The Tableau Prep Builder tool allows users to clean, shape and prepare data by
making it ease to delete, move or even merge fields from different data
sources. After cleaning data, Tableau Desktop and Tableau Public connect to the
clean data and are able to analyse it. Tableau Desktop allows users to connect
to basically any data source they want, like Excel spreadsheets, billion row
databases and even web APIs. In total, both Tableau Desktop and Tableau Public
support more than 80 different data sources including hundreds of web data
connectors used to grab data from e.g. HTML, JSON \& XML. Analysis can be done
by drag-and-drop and analysts can also ask questions inside the tool and get
the corresponding answer displayed as data. This really simplifies business
intelligence without the need of data warehouse expertise. Tableau Public on
the other hand can do the same as the desktop version but users can only share
dashboards and insights with others also using the public version - basically a
community, non profit, free edition of Tableau Desktop. After preparing and
connecting to data in order to build reports, analysis cannot be done by a
single person, so in order to share these reports across the business, a safe
and secure tool is needed. Also, collaboration between analysts and being able
to withstand numerous requests should be key factors of such a tool.
Tableau~Server and Tableau~Online offer all these aspects. The former is
deployed on-premise while the latter is hosted on Tableau Cloud. One downside
of Tableau Cloud which has to be considered is the storage limitation of 100GB
per site. Employees on the go can access data within the Tableau Mobile apps.
Tableau offers data visualisation out-of-the-box by dragging and dropping
columns and rows into desired fields and then choosing the desired
visualisation type, e.g. histogram, box-and-whisker and any further combination
between 30 different types are possible.

Except for Tableau Public, which is the only free version built to share data
in the Tableau ecosystem, every other tool needs to be purchased. In this case,
Tableau offers a package for individuals containing Desktop, Prep Builder and
Server or Online, which costs \$70/month per user. In case of teams and
organisations, packages are available from \textit{Viewer} to \textit{Explorer}
and \textit{Creator} ranging from \$12-\$70/month per user, where the first one
contains only basic functionality and the last one includes the full package.

Taking all these different packages into account, the best solution for SMEs
would be the Tableau Creator package with Tableau Online in order to avoid
having to manually set up and maintain a Tableau Server instance.

\subsection{Snowflake}

Snowflake is a data warehouse solution built on top of Amazon Web Services,
Microsoft Azure or Google Cloud Platform. It aims to fulfil the majority of
data analytics needs, such as data storage, data processing, data integration
and it provides analytics solutions. Snowflake offers multiple editions of
cloud data platform service: \textit{Standard Edition},
\textit{Enterprise Edition}, \textit{Business Critical Edition} and
\textit{Virtual Private Snowflake (VPS)}. The \textit{Standard Edition} offers
unlimited access to all standard features in the platform. Additionally the
\textit{Enterprise Edition} contains features designed especially for the needs
of large-scale organisations and enterprises. Furthermore, the
\textit{Business Critical Edition} and the \textit{Virtual Private Snowflake}
are for organisations who are dealing with extremely sensitive data. The
editions contain strict requirements and provide higher levels of data
protection. Snowflake also offers a 30-day trial with \$400 worth of free
usage. Before the login the user has to choose which cloud platform he wants
to use.

The Snowflake platform uses a unique architecture consisting of three layers:
database storage, query processing and cloud services. In the database storage
layer, data is loaded into the platform. After the loading process, the data
will be optimised, compressed and stored in cloud storage. Snowflake manages
all aspects of how the data is stored: the organisation, structure, metadata,
statistics and many more. The data objects are then accessible through SQL
query operations in the platform. In the query processing or virtual warehouse
layer, the query execution is performed. This is done by using “virtual
warehouses”. Each virtual warehouse is an independent compute cluster which
means that each warehouse has no impact on the performance of other virtual
warehouses. Warehouses come in different sizes ranging from XS (extra small) to
XXXL, depending on the organisations needs. Each size comes with different
credits which are important for pricing. Additionally the warehouses deliver
efficient BI solutions with an array of BI products, in total there are 23
different BI tools. The cloud service layer is responsible for the coordination
of activities across the platform, such as authentication, infrastructure
management, query parsing and optimisation and metadata management.

The pricing of theses layer depends on their actual usage. Snowflake offers two
different pricing options. The first one is “On Demand”: Customers are charged
a fixed rate for the services that are consumed and are billed every month. The
second one is “Pre-Purchased Capacity”. A company can pre-purchase capacity
which is then consumed on a monthly basis. Furthermore, Snowflake offers a
pricing overview for each cloud platform and region on their website. As an
example, a standard-level data warehouse running on Amazon Web Services in the
European region will cost \$2.70 per credit. In addition, 1TB of on-demand
storage costs \$45 per month.

In summary, the Snowflake data warehouse platform offers all the tools
necessary to store, retrieve, analyse and process data. The platform provides
good solutions for small businesses as well as for big organisations.

\end{document}
